\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0pt}{}[ -- ]
\renewcommand{\labelitemi}{--}

\begin{document}

\begin{center}
    {\LARGE \textbf{Louis Delacour}} \\
    \vspace{2mm}
    \small
    +33 7 60 99 29 16 \quad | \quad \texttt{louis.delacour.21@neoma-bs.com} \\
    LinkedIn: \href{https://www.linkedin.com/in/louis-delacour-70a530206/}{Louis-Delacour} \\ GitHub: \href{https://github.com/louisdelacour21}{louisdelacour21} \\
\end{center}

\vspace{0.05cm}

\section*{Education}
\textbf{\href{https://drive.google.com/drive/folders/1WzYw2E_0mfRNo33ZxSczjKHK1OzFjlqD?usp=sharing}{NEOMA Business School}}, Rouen, France \hfill 2021–2025 \\
\
\textit{Double Master’s – Master in Management \& MSc in Financial Markets and Risk Management} \\
\textit{GPA : 3.83} \\
Relevant courses: Credit/Market Risk, Big Data, Derivatives, Python, Machine Learning, Fintech and DeFi, FRM.

\textbf{\href{https://drive.google.com/drive/folders/1JJ2rY2UyCV3IehaStklcLUUJotaKgucl?usp=sharing}{Universität Regensburg}}, Germany \hfill 2024 \\
\textit{Exchange Semester – Financial Econometrics \& Computational Finance} \\
Distinction: First Class Honour \\
Courses: Financial reporting in the USA, Computational econometrics with Fortran, Business Analytics with Python, German economy 

\vspace{0.05cm}

\section*{Work Experience}

\textbf{Savours – Audit Start-up}, Marseille, France \\
\textit{Automation and Data Manager (Freelance)} \hfill Feb – Apr 2024
\begin{itemize}[leftmargin=1.5em, noitemsep]
    \item Designed 11 automation processes (Python, VBA, SQL), saving 7 hours/week/employee.
    \item Built client evaluation dashboards and reporting tools.
    \item Configured automation environment with external software partners.
\end{itemize}

\textbf{Savours – Audit Start-up}, Sheffield, UK \\
\textit{Auditor (6-month Off-cycle Internship)} \hfill Aug 2023 – Feb 2024
\begin{itemize}[leftmargin=1.5em, noitemsep]
    \item Audited 30 clients (Burger King, Pokawa, Subway) across UK and France.
    \item Managed a €5M portfolio of 150 clients.
    \item Conducted market analysis and built profitability KPIs with VBA.
\end{itemize}

\textbf{Pomona Group – Relais d’or Provence}, Rousset, France \\
\textit{Accountant (Fixed-term)} \hfill Jun – Aug 2021
\begin{itemize}[leftmargin=1.5em, noitemsep]
    \item Processed invoices, managed credit control and blocked accounts.
    \item Conducted weekly bank reconciliations and resolved litigation cases >€1.2M.
\end{itemize}

\vspace{0.05cm}

\section*{Extracurricular Activities}

\textbf{OPA Finance Club – Trading Department}, NEOMA BS \hfill Sep 2024 – Sep 2025
\begin{itemize}[leftmargin=1.5em, noitemsep]
    \item Carried out fundamental/technical analyses and paper trading strategies.
    \item Prepared for inter-university trading competitions.
\end{itemize}

\textbf{NEOMA Art Office – Treasurer} \hfill Oct 2021 – May 2023
\begin{itemize}[leftmargin=1.5em, noitemsep]
    \item Managed €200k budget across 12 art clubs; secured funding and state aid.
    \item Negotiated with suppliers and forecasted annual expenses.
\end{itemize}

\textbf{CPCS, ESCSF, SCH – Humanitarian Volunteering} \hfill 2017 – 2022
\begin{itemize}[leftmargin=1.5em, noitemsep]
    \item Fundraised in France and abroad, budgeted trips to Madagascar, Nepal, Cambodia.
    \item Served as treasurer in multiple missions.
\end{itemize}

\vspace{0.05cm}

\section*{Skills and Certifications}
\textbf{Technical Skills:} Python, Excel/VBA (Advanced) ; LaTex, SQL, Fortran (Intermediate)\\
\textbf{Languages:} French (Native), English (Fluent), Spanish (Intermediate) \\
\textbf{Certifications:} AMF Certification (France), Bloomberg Market Concepts, Python expert (Coding School).

\vspace{0.05cm}

\section*{Interests}
\textbf{Travel:} Over 10 countries; lived 6 months in the UK, 5 months in Germany, 2 months in Ireland \\
\textbf{Sports:} Rugby (7 years), Handball (6 years), Running (5 years) \\
\textbf{Other:} 2 years of dog handling training with a canine agency

\end{document}
